Results

### 2023-03-02 06_Paper/ER-ED/ERED_Stage2/Results.Rmd

To investigate, which variables can predict individual SVs of ER strategies, a multilevel model approach was chosen.
The ICC of the null model was $ICC=$ `r papaja::printnum(ICC_between_MLM_0)`, indicating that level-2 predictor subject accounted for `r papaja::printnum(round(ICC_between_MLM_0*100, digits = 1))` percent of total variance.
The preregistered model showed a correlation of $r=$ `r papaja::printnum(attr(summary(MLM_1)$varcor[1]$ID,"correlation")[1,2])` of the random effects subjects and recoded strategy ($BF10$ of the variable strategy: `r papaja::apa_print(MLM_1_BF)$statistic`).
Our model explained `r papaja::printnum(MLM1_r2[2])` percent of variance and thus we assumed our model was overfitted due to including recoded strategy as random slope.
We therefore set a new model without the recoded strategy as random slope factor to estimate the influence of predictors on SVs more precisely.
The second model followed the specification:

$$
\begin{split}
SV \sim \text{effort rating} + \text{arousal rating} + \text{utility rating} + corrugator \text{ activity} \\\ + levator \text{ activity} + (1 |subject)
\end{split}
$$

@@

>>>>

To investigate, which variables can predict individual SVs of ER strategies, a multilevel model approach was chosen.
The ICC of the null model was $ICC=$ `r papaja::printnum(ICC_between_MLM_0)`, indicating that level-2 predictor subject accounted for `r papaja::printnum(round(ICC_between_MLM_0*100, digits = 1))` percent of total variance.
The preregistered model showed a correlation of $r=$ `r papaja::printnum(attr(summary(MLM_1)$varcor[1]$ID,"correlation")[1,2])` of the random effects subjects and recoded strategy ($BF10$ of the variable strategy: `r papaja::apa_print(MLM_1_BF)$statistic`).
Our model explained `r papaja::printnum(MLM1_r2[2])` percent of variance and thus we assumed our model was overfitted due to including recoded strategy as random slope.
We therefore set a new model without the recoded strategy as random slope factor to estimate the influence of predictors on SVs more precisely.
The second model followed the specification: 
$$
\begin{split}
SV \sim \text{effort rating} + \text{arousal rating} + \text{utility rating} + corrugator \text{ activity} \\\ + levator \text{ activity} + (1 |subject)
\end{split}
$$

@@

We exploratory wanted to investigate the influence of self-control and the investment trait Need for Cognition (NFC) on individual SVs of ER strategies.
The starting point for this was the model reported before. 
Only predictors that had previously shown a significant association with SVs were included in the model together with level 2 predictors self-control and NFC.
The third model followed the specification:
$$
\begin{split}
SV \sim \text{effort rating} + \\text{utility rating} + corrugator \text{ activity} \\\ self-control + NFC + (1 |subject)
\end{split}
$$
